Analyzing Build Logs Using Programming by Example

### 2019-07-16 evaluation/Evaluation.Rmd
first kind of working IR extraction

escapeStringAsNotRegex <- function(x=character()){
  return(gsub("([.|()\\^{}+$*?]|\\[|\\])", "\\\\\\1", x))
}

nanosecsToTime <- function(ticks=numeric){
  sec <- ticks / 1e7
  return(as.POSIXct(sec, origin="1970-01-01", tz="UTC"))
}

@@

#data <- getDataFrameForResultsFile("android-failure-with-dependencies_ManualSelection.xml")
data <- getDataFrameForResultsFile("android-failure-with-dependencies_ManualSelection.xml")

@@

#plot(plot_data)
p <- ggplot(data = plot_data, aes(x = plot_data$ExampleCount, y = plot_data$ApplicationDuration)) + 
  geom_point(aes(col=plot_data$LearningDuration, size=plot_data$Accuracy)) + 
  labs(subtitle="", 
       y="application duration", 
       x="example count", 
       title="Scatterplot", 
       caption = "android-failure manual example selection") +
  scale_y_datetime(breaks = seq(from = min(data$ApplicationDuration), to = max(data$ApplicationDuration), by = 0.04), date_labels = "%OS3 sec")
  # scale_x_datetime(date_labels = "%M min")
plot(p)
```

>>>>

main_path <<- "/Users/Laci/Documents/Delft/master-thesis"

## load other modules
source(paste(main_path, "/evaluation/utilities.R", sep = ""))

@@

#data <- getDataFrameForResultsFile("android-failure-with-dependencies_ManualSelection.xml")
data <- getDataFrameForResultsFile("android-failure-with-dependencies_ChronologicalSelection.xml")

@@

#plot(plot_data)
p <- ggplot(data = plot_data, aes(x = plot_data$ExampleCount, y = plot_data$ApplicationDuration)) + 
  geom_point(aes(col=plot_data$LearningDuration, size=plot_data$Accuracy)) + 
  labs(subtitle="", 
       y="application duration", 
       x="example count", 
       title="Scatterplot", 
       caption = "android-failure chronological example selection") +
  scale_y_datetime(breaks = seq(from = min(data$ApplicationDuration), to = max(data$ApplicationDuration), by = 0.04), date_labels = "%OS3 sec")
  # scale_x_datetime(date_labels = "%M min")
ggsave("android-chronological.png", p) ## TODO make work
plot(p)
```

### 2019-07-16 paper/paper.tex
first kind of working IR extraction

problem, done in literature, why not eough? our approach
}

\review{Fixing a broken continuous integration (CI) build has a high priority for developers~\cite{vassallo2018un-break}, therefore decreasing the time until the green build state is restored improves the overall productivity of developers.

@@

During this assignment an engineer spends most of their time reading very long and verbose build logs, trying to retrieve the relevant information from between many uninteresting other lines.

A way to support them would be to extract the desired information and present it in a structured way.
One approach to realize such functionality are tools that employ handcrafted regular expressions to find the desired text parts within the build log.
However, creating these regular expressions is tedious, mentally complicated and usually error-prone task. Especially when they have to be maintained for long \textemdash \ reunderstanding old regular expressions is known to be a dreading task for developers.
Our goal is it to take this burden of programmers by enabling them to define extraction programs through simply giving examples of the desired extractions.

We implemented \todo{<toolname, ALBE?, Analyzing Logs By Example>}, a prototype for defining text extractions from build logs through examples.
After collecting a diverse set of build logs from Travis CI we designed a meta-model of the contained information.
Our evaluation of ALBE showed that it is able to define extractions for various desired informations, that it shortens development time in comparison to manual regular expression construction and ...
}

@@

@@

\subsection{Tools}

>>>>

problem, done in literature, why not enough? our approach
}

\review{Fixing a broken continuous integration (CI) build has a high priority for developers~\cite{vassallo2018un-break}, therefore decreasing the time until the success build state is restored improves the overall productivity of developers.

@@

During this assignment an engineer spends a lot of their time \todo{or: find percentage to cite} reading very long and verbose build logs, trying to retrieve the relevant information from between many uninteresting other lines. \todo{add anecdotal evidence, watchdog paper?}

A way to support them would be to extract the desired information and present it in a structured way.
One approach to realize such functionality are tools that employ handcrafted regular expressions to find the desired text parts within the build log.
However, creating these regular expressions is tedious, mentally complicated and usually error-prone task. Especially when they have to be maintained for long \textemdash \ reunderstanding old regular expressions is known to be a dreading task for developers.
Our goal is to evaluate an alternative way of taking this burden of programmers.
By simply giving examples of the desired extractions they should be able to define extraction programs.

We implement \todo{<toolname, ALBE?, Analyzing Logs By Example>}, a prototype for defining text extractions from build logs through examples.
After collecting a diverse set of build logs from Travis CI we design a meta-model of the contained information.
We evaluate ALBE on logs from selected GitHub repositories on the accuracy of extraction for a varying number and selection of in-output-examples.
Furthermore we compare the tool to classical information retrieval and plain keyword search.
Our evaluation of ALBE shows that it is able to define extractions for various desired informations, that it shortens development time in comparison to manual regular expression construction and ...
}

@@

\todo{More glue \& sentences that give an overview over the next paragraph}

\subsection{Bulidlogs Analysis Tools}

@@
